### 2018-11-26 Sections/physical_architectures_for_quantum_computing.tex
tiny

Let us describe the operation of a parity measurement\index{Parity measurements} device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of this design idea easily extend to other non-trivial operations, such as CNOT gates or QND measurements\index{Quantum non-demolition measurements}.

The key ingredient here is the cross-Kerr interaction, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators\index{Photon-number operators} for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength\index{Interaction strength}, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to photon-number and,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time\index{Interaction time}. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

Applying this operation between a coherent state and a photon-number state implements the two-mode transformation, 
\begin{align}
\hat{U}_\mathrm{ck} \ket\alpha \ket{n} = \ket{\alpha e^{i\theta n}} \ket{n}.	
\end{align}
Note that the phase-shift accumulated by the coherent state is proportional to the photon-number in the other mode, thereby entangling the two modes via their shared dependence on $n$.

@@

Consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances, and a coherent state in the shared qubus mode,
\begin{align}
\ket{\psi_\mathrm{in}} &= (\alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V})\ket\alpha.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}} &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

Clearly, since \mbox{$\braket{\alpha|\alpha e^{\pm i\theta}}\neq 0$}, there is some probability of error, associated with confusing the coherent basis states and hence their associated photonic qubit states. However, we asymptote towards perfect behaviour in the limit of large coherent qubus amplitudes, since,
\begin{align}	
\lim_{|\alpha|\to\infty}\braket{\alpha|\alpha e^{\pm i \theta}} = 0,
\end{align}
for any \mbox{$\theta\neq 0$}.

>>>>

Let us describe the operation of a parity measurement\index{Parity measurements} (i.e Bell analyser) device using weak non-linearities. This gate could subsequently be employed as a fusion gate\index{Fusion!Gates} (Sec.~\ref{sec:fusion_gates}) for building cluster states, and is therefore a resource for universal quantum computation. Simple extensions of this design idea easily extend to other non-trivial operations, such as CNOT and CZ gates or QND measurements\index{Quantum non-demolition measurements}.

The key ingredient here is the cross-Kerr interaction\index{Cross-Kerr Interaction}, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators\index{Photon-number operators} for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength\index{Interaction strength}, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to photon-number and,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time\index{Interaction time}. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

Applying this operation between a coherent state and a photon-number state implements the two-mode transformation, 
\begin{align}
\hat{U}_\mathrm{ck} \ket\alpha \ket{n} = \ket{\alpha e^{i\theta n}} \ket{n}.	
\end{align}
Note that the phase-shift accumulated by the coherent state is proportional to the photon-number in the other mode, thereby entangling the two modes via their shared dependence on $n$, effectively a photon-number-controlled phase-shift operation.

@@

Consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances, and a coherent state in the shared qubus mode,
\begin{align}
\ket{\psi_\mathrm{in}} &= (\alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V})\ket\alpha.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}} &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$ with non-zero $\theta$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

Clearly, since \mbox{$\braket{\alpha|\alpha e^{\pm i\theta}}\neq 0$}, there is some probability of error, associated with confusing the coherent basis states and hence their associated photonic qubit states. However, we asymptote towards perfect behaviour in the limit of large coherent qubus amplitudes, since,
\begin{align}	
\lim_{|\alpha|\to\infty}\braket{\alpha|\alpha e^{\pm i \theta}} = 0\,\,\forall\,\theta\neq 0.
\end{align}
